Classless Java: Tuning Java Interfaces

### 2015-11-24 paper/sections/CaseStudy.tex
Case Studies section ready to review

\section{Case Studies}
In this section we conduct three case studies which reveals various advantages
using \mixin annotation. 1st case study provides a easy and straightforward way
to solve the Expression Problem. 2nd case study models a simple game and the
comparison between our approach and others shows that code amount is reduced
tremendously using \mixin. 3rd case study models an embedded DSL for SQL
languages with fluent interfaces and shows that \mixin not only removes verbol
code for defining fluent interfaces but also does implicit refinement along
extension.

@@

Today we know of various solutions to the EP that either rely on \emph{new
  programming language features}
% ~\cite{chambers95multimethods, clifton00multiJava, madsen89virtual, nystrom06j,
%   bruce98astatically, McDirmid01jiazzi, garrigue98polymorphic,
%   zenger01extensible, loh06open, wehr11javaGI}, 
or can be used as \emph{design patterns}%~\cite{gof}
in existing languages.
% ~\cite{torgersen04theexpression, oliveira06extensible,
%  wouter08datatypes, oliveira09modular, oliveira12extensibility}. 
Now we show that the EP can be solved with our \mixin annotation in a trivial
way. We will use the canonical example of implementing arithmetic expressions
gradually to illustrate the usage.

@@

\subsection{A Small Game Example}
We now present a variant of a classic game example, which is often used to
evaluate reuse ability related to inheritance and design patterns. The code
using our approach and the solution by Bono et. al~\cite{bono14} in online, for
space constraints, we will omit it here. In the game, there is a player with the
goal of collecting as many coins as possible. She may enter a room with several
doors to be chosen among. This is a good example because it involves code reuse
(different kinds of doors inherit a common type, with different features and
behaviour), multiple inheritance (a special kind of door may require features
from two other door types). It also shows how to model symmetric sum, override
and alias as trait-oriented programming. Moreover, the code is provided in
~\cite{bono14} so that we can have a clear and fair comparison with our
approach, as shown in Table~\ref{table:codereduction}.

>>>>

\section{Case Studies}
In this section we conduct three case studies which reveals various advantages
using \mixin annotation. The first case study provides a easy and
straightforward way to solve the Expression Problem. The second one models a
simple game and the comparison between our approach and others shows that code
amount is reduced tremendously using \mixin. The third one models an embedded
DSL for SQL languages with fluent interfaces and shows that \mixin not only
removes verbol code for defining fluent interfaces but also does implicit
refinement along extension.

@@

Today we know of various solutions to the EP that either rely on \emph{new
  programming language features}
% ~\cite{chambers95multimethods, clifton00multiJava, madsen89virtual, nystrom06j,
%   bruce98astatically, McDirmid01jiazzi, garrigue98polymorphic,
%   zenger01extensible, loh06open, wehr11javaGI}, 
or can be used as \emph{design patterns}%~\cite{gof}
in existing languages. 
% ~\cite{torgersen04theexpression, oliveira06extensible,
%  wouter08datatypes, oliveira09modular, oliveira12extensibility}. 
A new solution~\cite{eptrivially} based on covariant type refinement solves EP
and works in Java-like languages. It does not introduce new language features,
does not even require generics support. However one of the limitation is certain
code verbosity caused by ``Final'' classes for instantiation. Now we show that
our \mixin annotation helps to remove these mechanical code in a trivial way. We
will use the canonical example of implementing arithmetic expressions gradually
as in \cite{eptrivially} to illustrate the usage.

@@

\subsection{A Small Game Example}
We now present a variant of a classic game example, which is often used to
evaluate code reuse ability related to inheritance and design patterns. The code
using our approach and the solution by Bono et. al~\cite{bono14} in online, for
space constraints, we will omit it here. In the game, there is a player with the
goal of collecting as many coins as possible. She may enter a room with several
doors to be chosen among. This is a good example because it involves code reuse
(different kinds of doors inherit a common type, with different features and
behaviour), multiple inheritance (a special kind of door may require features
from two other door types) and it also shows how to model operations
\texttt{symmetric sum}, \texttt{override} and \texttt{alias} as trait-oriented
programming. Moreover, the code is provided in ~\cite{bono14} so that we can
have a clear and fair comparison with our approach, as shown in
Table~\ref{table:codereduction}. We reduced the interfaces/classes used by
21.4\% (from 14 to 11) due to the replacement of instantiation classes with
generated \texttt{of} methods. We reduced source lines of code (SLOC) by
40\%. To ensure a fair comparison, we use the same code style as Bono's.
